LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-12-06 src/ms.tex
add recently submitted papers!

\lw{} has been developed with stellar-origin binary population studies in mind. We highlight two upcoming papers that use our package. Wagg et al.\ (in prep) investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars). They use \lw{} to evolve each synthesised source over the age of the Milky Way, make predictions about the LISA detectable population and explore how it varies with different binary physics assumptions. Additionally, Thiele et al.\ (in prep) examines the implications of assuming a metallicity-dependent binary fraction for the formation of close double white dwarfs (WDWDs) in the LISA frequency band. They use \lw{} to calculate the SNR of WDWDs and, in particular, apply a custom noise model that combines the LISA sensitivity curve from \citet{Robson+2019} with a new fit for the Galactic confusion noise based on their WDWD population.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{static/package_overview.png}
    \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
    \label{fig:package_overview}
\end{figure}

>>>>

\lw{} has been developed with stellar-origin binary population studies in mind. We highlight two recent papers that use our package. \citet{Wagg+2021} investigates several populations of potential LISA sources (double black holes, black hole neutron stars and double neutron stars). They use \lw{} to evolve each synthesised source over the age of the Milky Way, make predictions about the LISA detectable population and explore how it varies with different binary physics assumptions. Additionally, \citet{Thiele+2021} examines the implications of assuming a metallicity-dependent binary fraction for the formation of close double white dwarfs (WDWDs) in the LISA frequency band. They use \lw{} to calculate the SNR of WDWDs and, in particular, apply a custom noise model that combines the LISA sensitivity curve from \citet{Robson+2019} with a new fit for the Galactic confusion noise based on their WDWD population.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{static/package_overview.png}
    \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
    % \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{lwColour}\faFileImage}}}
    \label{fig:package_overview}
\end{figure}
